Exciting Internal Gravity Waves, Toy Problem

### 2018-03-23 presentations/Su_GM_032318.tex
small changes to presentation

    \begin{itemize}
        \item Top BC can be chosen Dirichlet $u_{1z}(x, L_z, t) = 0$,
            analytically tractable.

@@

        \item We use damping zone, add term $\rd{}{t}\vec{q} = L\vec{q}
            - f(z)\p*{\vec{q} - \vec{q}_0}$ where
            \begin{equation}
                f(z) =
                \begin{cases}
                    \Gamma \s*{
                        1 - \frac{\p*{z - L_z}^2}
                            {\p*{z_{damp} - L_z}^2}
                    }
                        & z > z_{damp}\\
                    0 & z < z_{damp}
                \end{cases}.
            \end{equation}
    \end{itemize}
\end{frame}

@@

        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_2.png}
        \end{subfigure}
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_3.png}
        \end{subfigure}
        \caption{Agreement of numerical and analytical solution at four adjacent
        snapshots.}\label{fig:sponge_agree}
    \end{figure}
\end{frame}

>>>>

    \begin{itemize}
        \item Top BC can be chosen Dirichlet $u_{1z}(x, L_z, t) = 0$,
            analytically tractable as linear combination of $\pm k_z$ solutions.

@@

        \item We use damping zone, add term $\pd{}{t}\vec{q} = L\vec{q}
            - f(z)\p*{\vec{q} - \vec{q}_0}$ where
            \begin{equation}
                f(z) =
                \begin{cases}
                    \Gamma \s*{
                        1 - \frac{\p*{z - L_z}^2}
                            {\p*{z_{damp} - L_z}^2}
                    }
                        & z > z_{damp}\\
                    0 & z < z_{damp}
                \end{cases}.
            \end{equation}
    \end{itemize}
\end{frame}

@@

        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_2.png}
        \end{subfigure}
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_3.png}
        \end{subfigure}
        \caption{Numerical and analytical solutions agree. Numerics chooses
        $v_{gz} > 0$.}\label{fig:sponge_agree}
    \end{figure}
\end{frame}
